---
title: "Frameworks Final Project: Data Cleaning"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,tidy = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE}
library(knitr);  library(DT);library(ggplot2);library(data.table); library(tidytext); library(stringr)
library(qdapTools)
```

```{r constants}
name = "Name"
city.name = "City"
cuisine.name = "Cuisine Style"
ranking.name = "Ranking"
rating.name = "Rating"
price.name = "Price Range"
number.reviews.name = "Number of Reviews"
review.name = "Reviews"
```

```{r load the data}
dat <- fread(input ='Data/TA_restaurants_curated.csv', verbose = FALSE)
```

```{r functions}
# specialized function to calculate the numberic value of '$,$$,$$$,$$$$` ratings 
replace.value = function (data, colname, pattern = '-' ){
number = vector() 
for ( i in 1:nrow(dat)) {
 if (is.na(str_match(string = data[i, get(colname)], pattern = '-'))) {
     number[i] = nchar(data[i, get(colname)])
 } else { number[i] = ((nchar(data[i, get(colname)]) - 3) / 2)
  }
}
print(number)
}
mean.missing <- function(x) {
 return(mean(is.na(x)))
}
```

```{r Drop columns }
# Drop columns 
dat$URL_TA <- NULL
```

## Exploring missing data 
```{r missing data exploration}
paste0(round(mean.missing(x = dat) * 100,2), '% of all the data is missing')
# missing data by columns 
dat[, lapply(X = .SD, mean.missing)]
```

### Exploring ranking
```{r ranking exploration}
# number of ranking in each category  
ranking.count <- dat[, .(count = .N), by = ranking.name]
# view the data 
head(ranking.count,10)
```
```{r echo=FALSE}
# missing value analysis 
paste0('There are ', max(ranking.count$Ranking, na.rm = TRUE), ' rankings in the data set', ' with an average count of ' ,round(ranking.count[!is.na(ranking.count$Ranking), mean(count)],2), ' in each rank, not including the NAs, which has ', ranking.count[is.na(ranking.count$Ranking),]$count, ' values which represents ',round(
(ranking.count[!is.na(ranking.count$Ranking), mean(count)] / nrow(ranking.count)) * 100,2) , '% of the entire dataset')
```


The rank value represents the Rank of the restaurant among the total number of restaurants in the city, and there are number of reasons as to why it could be missing: 

- The restaurant is new, or no one has reviewed it yet. A solution that makes sense for the missing data is to the missing value should have a rank a level lower than the last rank in the data.  


```{r addressing rank}
# adding +1 to the max ranking to fix na's 
max.ranking <- max(dat$Ranking, na.rm = TRUE)
dat[is.na(get(ranking.name)), eval(ranking.name) :=  max.ranking + 1]
# count Na's in ranking
sum(is.na(dat$Ranking))
```


# exploring Rating

```{r}
hist(dat$Rating, xlab = 'Ratings', main = 'Distribution of Ratings', col = 'lightblue')
ratings.count <- dat[,.(count = .N, `Percentage` = (.N/nrow(dat)) * 100), by = rating.name]
ratings.count
```

The data desription indicates that the rating for rating range from 1-5 yet we have a 41 values that are -1 in the dataset. 

How can we address this: 
- replace the missing values with the mean, median
- replace the missing values based on stratisfied random sampling based on the percentage of the range 1-5 
- random numbers between 1-5
- replace with a value of 0 or 1

Before we can make that descision, lets have look at the those data


```{r}
summary(dat[get(rating.name) < 1 | is.na(get(rating.name))])
```

The restaurants that do not have a ratings also didn't have a ranking. They are either new or no one has reviwed them yet. The best course of action is to replace with 0. 


```{r}
# replacing negative and na values with 0
dat[get(rating.name) < 1 | is.na(get(rating.name)), eval(rating.name) := 0]
hist(dat$Rating, xlab = 'Ratings', main = 'Distribution of Ratings', col = 'lightblue', breaks = 10)
ratings.count <- dat[,.(count = .N, `Percentage` = (.N/nrow(dat)) * 100), by = rating.name]
ratings.count
```

## Number of reviews 


```{r number of reviews}
number.of.reviews.count <- dat[,.(count = .N), by = number.reviews.name]
setorder(number.of.reviews.count,-count)
ggplot(data = number.of.reviews.count, aes(x = `Number of Reviews` , y = count)) + geom_line() + theme_classic()
# top 5 of review counts 
head(number.of.reviews.count)
# count of number of NA 
dat[is.na(get(number.reviews.name)),.N, by = number.reviews.name]
# summary 
summary(dat$`Number of Reviews`)
```


The most likely reason that a restaurant wouldn't have a review is because no one botherered to review it.

The best way to fix it is to replace it with 0 
```{r}
# evaluate number of reviews NA as 0 
dat[is.na(get(number.reviews.name)), eval(number.reviews.name):= 0]
```

```{r}
# missing data by columns 
dat[, lapply(X = .SD, mean.missing)]
```
no more missing data

### price range 
```{r}
# price count distribution
price.count <- dat[, .N, by = price.name]
price.count
```

```{r include=FALSE}
# evaluating characters to numeric 
value <- replace.value(data = dat, colname = price.name)
dat$`Price Range` <- value
```

```{r}
# result 
price.count <- dat[, .N, by = price.name]
price.count
```

## reviews 
```{r}
head(dat$Reviews)
```

```{r Split}
#Split the cuisine style
the.pattern = "'"
the.pattern.start.end= "\\[|\\]"
pattern.inside=","
dat[, eval(cuisine.name) := gsub(pattern = the.pattern, replacement = "", x = get(cuisine.name))]
dat[, eval(cuisine.name) := gsub(pattern = the.pattern.start.end, replacement = "", x = get(cuisine.name))]
newdat= mtabulate(strsplit(as.character(dat[[cuisine.name]]), ","))
finaldat= (cbind(dat, newdat))
```

# Reviews 
```{r}
library(stringr)
```


```{r}
write.csv(x = finaldat, file = 'Data/TA_restaurants_curated_clean.csv')
```

